Characterization of an anionic membrane mimetic with natural phospholipid content and magnetic orienting capabilities

### 2020-09-02 revision_cover_letter.tex
Corregido un error en el lenguage en la carta

  Regarding the observations both of the reviewers, we have made multiple changes to
  our manuscript in order to amend the issues found by them, they are listed as
  follows:

>>>>

  Regarding the observations made by both of the reviewers, we have made multiple changes to
  our manuscript in order to amend the issues they found, and they are listed as
  follows:
